---
output: html_document
params:
  set_title: "The Task Space: An Integrative Framework for Team Research"
---

---
title: `r params$set_title`
---
*Management Science*, Accepted October 2025

Author(s): Xinlan Emily Hu, Mark E. Whiting, Linnea Gandhi, Duncan J. Watts, and Abdullah Almaatouq

# Abstract

Research on teams spans many diverse contexts, but integrating knowledge from heterogeneous sources is challenging because studies typically examine different tasks that cannot be directly compared. Most investigations involve teams working on just one or a handful of tasks, and researchers lack principled ways to quantify how similar or different these tasks are from one another. We address this challenge by introducing the “Task Space,” a multidimensional framework that represents tasks along 24 theoretically-motivated dimensions. To demonstrate its utility, we apply the Task Space to a fundamental question in teams research: when do interacting groups outperform individuals? Using the Task Space to systematically sample 20 diverse tasks, we conducted an integrative experiment with 1,231 participants working at three complexity levels, either individually or in groups of three or six (180 experimental conditions). We find striking heterogeneity in group advantage, with groups performing anywhere from three times worse to 60% better than the best individual working alone, depending on the task context. Task Space dimensions significantly outperform traditional typologies in predicting group advantage on unseen tasks. Additionally, our models reveal theoretically meaningful interactions between task features; for example, group advantage on creative tasks depends on whether the answers are objectively verifiable. The Task Space ultimately enables researchers to move beyond isolated findings to identify boundary conditions and build cumulative knowledge about team performance.

# Understanding teams requires understanding their tasks.

> Is a larger group more effective than a smaller group? Are groups more productive than individuals? Can AI enhance team performance?

The answers to many critical questions about teamwork depend on the task being performed. Consequently, researchers and practitioners alike need a practical way to quantify when two tasks are similar or different from one another --- and hence to understand how findings from one task might generalize to another.

The Task Space provides a framework to do exactly that. It allows researchers to represent any task as a point in a 24-dimensional space, where each dimension corresponds to a theoretically-motivated feature of the task.

Potential applications of the Task Space include:

-  Intelligently **selecting tasks for experiments** (for example, to [maximize the diversity of tasks selected](./task space resources/choose-10-tasks.ipynb), or to focus on tasks with special properties);
-  **Quantifying task similarities and differences**, both to understand the generalizability of findings and to control for task features in statistical analysis;
-  **Building "task-sensitive" theories** that account for how team behavior varies as a function of task features;
-  **Designing team environments** that are tailored to the specific task at hand (for example, assigning actors to tasks for which they have a comparative advantage).

# Using the Task Space

As a starting point, we built a ``map'' of the space: a repository of 102 laboratory tasks from the interdisciplinary literature on group performance, rated along the 24 Task Space dimensions using a crowd annotation process. 

## Download the Task Map
The Task Map (102 x 24 matrix) can be downloaded here: [`task_map.csv`](./processed_data/task_map.csv).

## 24 Task Dimensions
The 24 dimensions are detailed here: ['24_dimensions_clean.csv'](./task space resources/24_dimensions_clean.csv).

## 102 Tasks
The 102 tasks and their descriptions are detailed here: [`102_tasks_with_sources_clean.csv`](./task space resources/102_tasks_with_sources_clean.csv).

# Annotating New Tasks

We also provide documentation on how to annotate new tasks, including the annotation rubric and the code used to generate the Task Space from raw annotations.

- The questions displayed to raters can be found here: [`questions_displayed_to_raters.csv`](./task space resources/questions_displayed_to_raters.csv).

- Resources for rater training and managing the annotation pipeline can be found here: [`rating pipelines/`](./task space resources/rating pipelines/)

- The code used to generate the Task Space from raw annotations can be found here: [`generate_task_map_from_raw.Rmd`](./analysis/analysis_task_space/generate_task_map_from_raw.Rmd).

# Accessing our Full Reproduction package

Our full reproduction package is hosted [on GitHub](https://github.com/Watts-Lab/task-mapping).

# Visualizing the Task Map

The following interactive visualizer allows you to explore the Task Map in two dimensions using PCA, and to conduct k-means clustering on the underlying 24-dimensional space. You can choose different values of *k*, and mouse over each dot to see the name of the task.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(e1071)
library(plotly)
library(dplyr)
library(tidyverse)
```

```{r echo=F, out.width="100%"}
knitr::include_app("https://xehu.shinyapps.io/interactive-task-map/")
```

# Team
- [Xinlan Emily Hu](https://xinlanemilyhu.com) (Corresponding Author)
- [Mark Whiting](https://whiting.me/)
- [Linnea Gandhi](https://www.linneagandhi.com/)
- [Duncan J. Watts](https://duncanjwatts.com/)
- [Abdullah Almaatouq](http://amaatouq.io/) (Corresponding Author)

This work was also created with the support from many other people, including many research assistants at the University of Pennsylvania, as well as the with labor of Amazon Mechanical Turk workers. 

This project is part of the [group dynamics / integrative experiments research](https://css.seas.upenn.edu/project/integrative-experiments/) at the [Computational Social Science Lab at Penn](https://css.seas.upenn.edu). You can learn more about our lab [here](https://css.seas.upenn.edu/people/). 