---
title: "P3 analysis"
author: "Mark Whiting"
date: "2/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(tidyr)
library(readr)
library(pwr)
library(readr)
library(irr)
```
```{r dataStructure, include=FALSE}
rawData <- read_csv("Pilot 3 data.csv") 

questions <- rawData %>% 
  filter(
    StartDate == "Start Date"
  ) %>% 
  select(contains("Q")) %>% 
  gather(ID, Question) %>% 
  separate(ID,c("TaskID","QID","EID")) %>%
  unite("QuestionID",QID,EID,na.rm=TRUE,sep="") %>%  
  filter(!grepl("Q",TaskID)) %>%
  filter(!grepl("Q44",Question)) %>% 
  mutate(
    TaskID = as.numeric(TaskID),
    QuestionID = as.numeric(sub("Q","",QuestionID))
  )

tasks <- questions %>% 
  filter(QuestionID == 3) %>% 
  separate(Question, c("Task","Question"), sep = " - ") %>% 
  select(contains("Task"))

questions <- questions %>% 
  left_join(tasks) %>% 
  group_by(Task) %>% 
  mutate(
    Question = sub(paste(" *-* *",Task," - ",sep = ""),"",Question)
  ) %>% 
  ungroup() %>%
  select(contains("Question")) %>% 
  distinct() %>% 
  mutate(
    Question = sub("For the next few questions answer the degree to which each aspect can be achieved with \\[Field-1\\].","",Question),
    Question = sub("\\[Field-1\\]","the task",Question),
    ResponseType = case_when(
      QuestionID == 6 ~ "mental",
      QuestionID == 7 ~ "intellective",
      QuestionID > 50 ~ "l5pt",
      QuestionID == 32 ~ "agree",
      QuestionID == 44 ~ "character", 
      TRUE ~ "yn" 
    ),
    Question = paste(ResponseType, QuestionID, Question, sep = " - ")
  ) 

mentalType <- function(column) {ordered(column,levels=c("Entirely mental effort", "Moderately mental effort", "About 50–50", "Moderately motor effort", "Entirely motor effort"))}
intelletiveType <- function(column) {factor(column)}
l5ptType <- function(column) {ordered(column,levels=c("Definitely false", "Probably false", "Neither true nor false", "Probably true", "Definitely true"))}
agreeType <- function(column) {ordered(column,levels=c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree", "Somewhat agree", "Strongly agree"))}
characterType <- function(column) {as.character(column)}
ynType <- function(column) {ordered(column,levels=c("No","Yes"))}

responses <- rawData %>%
  filter(Finished == "True") %>% 
  select(ResponseId, contains("Q")) %>% 
  filter(!is.na(`2_Q32`)) %>% 
  gather(Question,Answer,-ResponseId) %>% 
  separate(Question,c("TaskID","QID","EID")) %>%
  unite("QuestionID",QID,EID,na.rm=TRUE,sep="") %>%  
  filter(!grepl("Q",TaskID)) %>% 
  mutate(
    TaskID = as.numeric(TaskID),
    QuestionID = as.numeric(sub("Q","",QuestionID))
  ) %>%
  left_join(questions) %>% 
  left_join(tasks) %>% 
  filter(!is.na(QuestionID)) %>% 
  select(-TaskID, -QuestionID, -ResponseType) %>%
  spread(Question,Answer) %>% 
  mutate_at(vars(contains("yn - ")),ynType) %>%
  mutate_at(vars(contains("character - ")),characterType) %>%
  mutate_at(vars(contains("agree - ")),agreeType) %>%
  mutate_at(vars(contains("l5pt - ")),l5ptType) %>%
  mutate_at(vars(contains("mental - ")),mentalType) %>%
  mutate_at(vars(contains("intellective - ")),intelletiveType) %>% 
  select(-contains("character - "))
```
We first build several core data frames:

- **Tasks** lists the `r dim(tasks)[1]` tasks we studied and their IDs 
- **Questions** lists the `r dim(questions)[1]` questions, their IDs and the answer type they use
- **Responses** lists `r dim(responses)[1]` total responses, broken out by task-respondant pairs, with questions as columns. These encompass responses from `r length(unique(responses$ResponseId))` unique individuals.
```{r analysis, include = FALSE}
# Accepts a table, a column name to group by, and a column name pattern to select subjects. 
calculateFleissKappa = function(dataTable, rowGroup, colPattern) {
  rowGroups = unique(dataTable[rowGroup])
  apply(rowGroups,1,function(group){
    groupTable = dataTable %>% filter(!!as.symbol(rowGroup) == group)
    cols = as.data.frame(names(groupTable %>% select(matches(colPattern))))
    return(apply(cols,1,function(column){
      colTable = groupTable %>% select(!!as.symbol(column))
      return(kappam.fleiss(t(as.matrix(colTable)))$value)
    }))
  })
}

# Accepts a table, a column name to group by, and a column name pattern to select subjects. 
calculateKrippAlpha = function(dataTable, rowGroup, colPattern) {
  rowGroups = unique(dataTable[rowGroup])
  apply(rowGroups,1,function(group){
    groupTable = dataTable %>% filter(!!as.symbol(rowGroup) == group)
    cols = as.data.frame(names(groupTable %>% select(matches(colPattern))))
    return(apply(cols,1,function(column){
      colTable = groupTable %>% select(!!as.symbol(column))
      return(kripp.alpha(as.matrix(colTable))$value)
    }))
  })
}

fleissKappaMatrix = calculateFleissKappa(responses,"Task"," - ")
kripAlphaMatrix = calculateKrippAlpha(responses,"Task"," - ")
```
To evaluate the inter rater reliability, we compute Fleiss' Kappa 

`r round(fleissKappaMatrix,2)`

and Krippendorf's Alpha 

`r round(kripAlphaMatrix,2)`

for each task-question pair (a `r dim(fleissKappaMatrix)` matrix, because one question was dropped due to being a free text response). However, this does not give us what we want as each position in these results is calculated from a 1 dimensional vector, which is not how these statistics are intended to be used. All this tells us is that 

*Note that in Fleiss' Kappa, `NA` for a 1 dimensional vector is similar to 1, as in no variance across respondants. Kripendorf's Alpha does this correctly and shows 1 in those positions.*
```{r}
subsetResponse <- responses %>% select(ResponseId,Task,contains("mental")) %>% spread(ResponseId, `mental - 6 - What is the ratio of mental to motor effort in the task?\nFor example, basketball requires almost entirely motor effort, while calculating a tip in a restaurant is almost entirely mental effort.`)
names(subsetResponse)
kappam.fleiss(subsetResponse)
```

