---
title: "P3 analysis"
author: "Mark Whiting"
date: "2/26/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(tidyr)
library(readr)
library(pwr)
library(readr)
library(irr)
```
```{r dataStructure, include=FALSE}
rawData <- read_csv("Pilot 3 data.csv") 

questions <- rawData %>% 
  filter(
    StartDate == "Start Date"
  ) %>% 
  select(contains("Q")) %>% 
  gather(ID, Question) %>% 
  separate(ID,c("TaskID","QID","EID")) %>%
  unite("QuestionID",QID,EID,na.rm=TRUE,sep="") %>%  
  filter(!grepl("Q",TaskID)) %>%
  filter(!grepl("Q44",Question)) %>% 
  mutate(
    TaskID = as.numeric(TaskID),
    QuestionID = as.numeric(sub("Q","",QuestionID))
  )

tasks <- questions %>% 
  filter(QuestionID == 3) %>% 
  separate(Question, c("Task","Question"), sep = " - ") %>% 
  select(contains("Task"))

questions <- questions %>% 
  left_join(tasks) %>% 
  group_by(Task) %>% 
  mutate(
    Question = sub(paste(" *-* *",Task," - ",sep = ""),"",Question)
  ) %>% 
  ungroup() %>%
  select(contains("Question")) %>% 
  distinct() %>% 
  mutate(
    Question = sub("For the next few questions answer the degree to which each aspect can be achieved with \\[Field-1\\].","",Question),
    Question = sub("\\[Field-1\\]","the task",Question),
    ResponseType = case_when(
      QuestionID == 6 ~ "mental",
      QuestionID == 7 ~ "intellective",
      QuestionID > 50 ~ "l5pt",
      QuestionID == 32 ~ "agree",
      QuestionID == 44 ~ "character", 
      TRUE ~ "yn" 
    ),
    # Question = paste(ResponseType, QuestionID, Question, sep = " - ")
  ) 

write_csv(questions,"questions.csv")

mentalType <- function(column) {ordered(column,levels=c("Entirely mental effort", "Moderately mental effort", "About 50–50", "Moderately motor effort", "Entirely motor effort"))}
intelletiveType <- function(column) {factor(column)}
l5ptType <- function(column) {ordered(column,levels=c("Definitely false", "Probably false", "Neither true nor false", "Probably true", "Definitely true"))}
agreeType <- function(column) {ordered(column,levels=c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree", "Somewhat agree", "Strongly agree"))}
characterType <- function(column) {as.character(column)}
ynType <- function(column) {ordered(column,levels=c("No","Yes"))}

responsesAll <- rawData %>%
  filter(Finished == "True") %>% 
  select(ResponseId, contains("Q")) %>% 
  filter(!is.na(`2_Q32`)) %>% 
  gather(Question,Answer,-ResponseId) %>% 
  separate(Question,c("TaskID","QID","EID")) %>%
  unite("QuestionID",QID,EID,na.rm=TRUE,sep="") %>%  
  filter(!grepl("Q",TaskID)) %>% 
  mutate(
    TaskID = as.numeric(TaskID),
    QuestionID = as.numeric(sub("Q","",QuestionID))
  ) %>%
  left_join(questions) %>% 
  left_join(tasks) %>% 
  filter(!is.na(QuestionID)) %>% 
  select(-TaskID, -QuestionID, -ResponseType) %>%
  spread(Question,Answer) %>% 
  mutate_at(vars(contains("yn - ")),ynType) %>%
  mutate_at(vars(contains("character - ")),characterType) %>%
  mutate_at(vars(contains("agree - ")),agreeType) %>%
  mutate_at(vars(contains("l5pt - ")),l5ptType) %>%
  mutate_at(vars(contains("mental - ")),mentalType) %>%
  mutate_at(vars(contains("intellective - ")),intelletiveType) 

unique(responsesAll$`Categorize the task among the options below:`)


responses = responsesAll %>% 
  select(-contains("character - "))
```
We first build several core data frames:

- **Tasks** lists the `r dim(tasks)[1]` tasks we studied and their IDs 
- **Questions** lists the `r dim(questions)[1]` questions, their IDs and the answer type they use
- **Responses** lists `r dim(responses)[1]` total responses, broken out by task-respondant pairs, with questions as columns. These encompass responses from `r length(unique(responses$ResponseId))` unique individuals.
```{r analysis, include = FALSE}
# Accepts a table, a column name to group by, and a column name pattern to select subjects. 
calculateFleissKappa = function(dataTable, rowGroup, colPattern) {
  rowGroups = unique(dataTable[rowGroup])
  apply(rowGroups,1,function(group){
    groupTable = dataTable %>% filter(!!as.symbol(rowGroup) == group)
    cols = as.data.frame(names(groupTable %>% select(matches(colPattern))))
    return(apply(cols,1,function(column){
      colTable = groupTable %>% select(!!as.symbol(column))
      return(kappam.fleiss(t(as.matrix(colTable)))$value)
    }))
  })
}

# Accepts a table, a column name to group by, and a column name pattern to select subjects. 
calculateKrippAlpha = function(dataTable, rowGroup, colPattern) {
  rowGroups = unique(dataTable[rowGroup])
  apply(rowGroups,1,function(group){
    groupTable = dataTable %>% filter(!!as.symbol(rowGroup) == group)
    cols = as.data.frame(names(groupTable %>% select(matches(colPattern))))
    return(apply(cols,1,function(column){
      colTable = groupTable %>% select(!!as.symbol(column))
      return(kripp.alpha(as.matrix(colTable))$value)
    }))
  })
}

fleissKappaMatrix = calculateFleissKappa(responses,"Task"," - ")
kripAlphaMatrix = calculateKrippAlpha(responses,"Task"," - ")
```
To evaluate the inter rater reliability, we compute Fleiss' Kappa 

`r round(fleissKappaMatrix,2)`

and Krippendorf's Alpha 

`r round(kripAlphaMatrix,2)`

for each task-question pair (a `r dim(fleissKappaMatrix)` matrix, because one question was dropped due to being a free text response). However, this does not give us what we want as each position in these results is calculated from a 1 dimensional vector, which is not how these statistics are intended to be used. All this tells us is that 

*Note that in Fleiss' Kappa, `NA` for a 1 dimensional vector is similar to 1, as in no variance across respondants. Kripendorf's Alpha does this correctly and shows 1 in those positions.*

So, we'd rather do this for subsets of the data, e.g. for each task, find the agreemt across raters and questions, or for each question, find the agreement across raters and tasks, or even, for each rater, find the agremeent across tasks and questions. In the next section, these assesments are performed.

```{r per task agreement, include=FALSE}
questionNames = names(responses %>% select(-ResponseId, -Task))
perTaskAgreement = responses %>% group_by(Task) %>% 
  summarise(
    fleissKappa = kappam.fleiss(t(cbind(
      .data[[questionNames[1]]],
      .data[[questionNames[2]]],
      .data[[questionNames[3]]],
      .data[[questionNames[4]]],
      .data[[questionNames[5]]],
      .data[[questionNames[6]]],
      .data[[questionNames[7]]],
      .data[[questionNames[8]]],
      .data[[questionNames[9]]],
      .data[[questionNames[10]]],
      .data[[questionNames[11]]],
      .data[[questionNames[12]]],
      .data[[questionNames[13]]],
      .data[[questionNames[14]]],
      .data[[questionNames[15]]],
      .data[[questionNames[16]]],
      .data[[questionNames[17]]],
      .data[[questionNames[18]]],
      .data[[questionNames[19]]],
      .data[[questionNames[20]]],
      .data[[questionNames[21]]],
      .data[[questionNames[22]]],
      .data[[questionNames[23]]],
      .data[[questionNames[24]]],
      .data[[questionNames[25]]],
      .data[[questionNames[26]]]
      )))$value,
    kripAlpha = kripp.alpha((cbind(
      .data[[questionNames[1]]],
      .data[[questionNames[2]]],
      .data[[questionNames[3]]],
      .data[[questionNames[4]]],
      .data[[questionNames[5]]],
      .data[[questionNames[6]]],
      .data[[questionNames[7]]],
      .data[[questionNames[8]]],
      .data[[questionNames[9]]],
      .data[[questionNames[10]]],
      .data[[questionNames[11]]],
      .data[[questionNames[12]]],
      .data[[questionNames[13]]],
      .data[[questionNames[14]]],
      .data[[questionNames[15]]],
      .data[[questionNames[16]]],
      .data[[questionNames[17]]],
      .data[[questionNames[18]]],
      .data[[questionNames[19]]],
      .data[[questionNames[20]]],
      .data[[questionNames[21]]],
      .data[[questionNames[22]]],
      .data[[questionNames[23]]],
      .data[[questionNames[24]]],
      .data[[questionNames[25]]],
      .data[[questionNames[26]]]
      )))$value
  )
```

```{r per question agreement, include=FALSE}
perQuestionAgreement = as.data.frame(Reduce(rbind,Map(function(Question) {
  return(cbind(
    Question,
    fleissKappa = kappam.fleiss(responses %>% 
                                  select(ResponseId, Task, !!Question) %>% 
                                  spread(ResponseId,!!Question))$value,
    kripAlpha = kripp.alpha(t(responses %>% 
                                  select(ResponseId, Task, !!Question) %>% 
                                  spread(ResponseId,!!Question)))$value
    ))
},questionNames)))

# These end up as factors because of cbind, so we coerce them to numerics. Note that we do this via character because otherwise they are coerced as the numerical value of the ordinal. 
perQuestionAgreement <- perQuestionAgreement %>% mutate(
  fleissKappa = as.numeric(as.character(fleissKappa)), 
  kripAlpha = as.numeric(as.character(kripAlpha))
  )
```

```{r per rater agreement, include=FALSE}
perRaterAgreement = responses %>% group_by(ResponseId) %>% 
  summarise(
    fleissKappa = kappam.fleiss(t(cbind(
      .data[[questionNames[1]]],
      .data[[questionNames[2]]],
      .data[[questionNames[3]]],
      .data[[questionNames[4]]],
      .data[[questionNames[5]]],
      .data[[questionNames[6]]],
      .data[[questionNames[7]]],
      .data[[questionNames[8]]],
      .data[[questionNames[9]]],
      .data[[questionNames[10]]],
      .data[[questionNames[11]]],
      .data[[questionNames[12]]],
      .data[[questionNames[13]]],
      .data[[questionNames[14]]],
      .data[[questionNames[15]]],
      .data[[questionNames[16]]],
      .data[[questionNames[17]]],
      .data[[questionNames[18]]],
      .data[[questionNames[19]]],
      .data[[questionNames[20]]],
      .data[[questionNames[21]]],
      .data[[questionNames[22]]],
      .data[[questionNames[23]]],
      .data[[questionNames[24]]],
      .data[[questionNames[25]]],
      .data[[questionNames[26]]]
      )))$value, 
    kripAlpha = kripp.alpha((cbind(
      .data[[questionNames[1]]],
      .data[[questionNames[2]]],
      .data[[questionNames[3]]],
      .data[[questionNames[4]]],
      .data[[questionNames[5]]],
      .data[[questionNames[6]]],
      .data[[questionNames[7]]],
      .data[[questionNames[8]]],
      .data[[questionNames[9]]],
      .data[[questionNames[10]]],
      .data[[questionNames[11]]],
      .data[[questionNames[12]]],
      .data[[questionNames[13]]],
      .data[[questionNames[14]]],
      .data[[questionNames[15]]],
      .data[[questionNames[16]]],
      .data[[questionNames[17]]],
      .data[[questionNames[18]]],
      .data[[questionNames[19]]],
      .data[[questionNames[20]]],
      .data[[questionNames[21]]],
      .data[[questionNames[22]]],
      .data[[questionNames[23]]],
      .data[[questionNames[24]]],
      .data[[questionNames[25]]],
      .data[[questionNames[26]]]
      )))$value
  )
```

```{r message=FALSE, warning=FALSE}
ggplot(perTaskAgreement,aes(Task,fleissKappa)) +
  geom_col() + 
  geom_point(aes(x = perTaskAgreement$Task, y = perTaskAgreement$kripAlpha)) + 
  coord_flip() + 
  theme_minimal()

ggplot(perQuestionAgreement,aes(Question,fleissKappa)) +
  geom_col() + 
  geom_point(aes(x = perQuestionAgreement$Question, y = perQuestionAgreement$kripAlpha)) + 
  scale_x_discrete(labels=substring(perQuestionAgreement$Question,0,40)) + 
  coord_flip() + 
  theme_minimal()

ggplot(perRaterAgreement,aes(ResponseId,fleissKappa)) +
  geom_col() + 
  geom_point(aes(x = perRaterAgreement$ResponseId, y = perRaterAgreement$kripAlpha)) + 
  coord_flip() + 
  theme_minimal()
```

```{r agreement studies}

# Expanding the 'per question' design
mine = kappam.fleiss(
  (responses %>% select(questionNames[26],Task,ResponseId) %>% spread(ResponseId,questionNames[26])),
  detail = TRUE)$detail

as.data.frame(mine) %>% 
  filter(Var2 == "Kappa") %>% 
  mutate(
    Task = Var1,
    fleissKappa = Freq
  ) 

# percentage of agreements for each qestion for each task - agreement at a random guess
ourMeasure <- responses %>% 
  select(-ResponseId) %>% 
  group_by(Task) %>% 
  summarize_each(function(col) {
    agreement = mean((outer(col,col,function(x, y) as.integer(x==y)) %*% replicate(n(), 1)) / n())
    random = 1/nlevels(col)
    return(agreement - random)
  })  %>% gather(Question,Agreement,-Task)

ggplot(ourMeasure, aes(Task,Question,fill = Agreement)) + 
  geom_tile() + 
  geom_text(aes(label=paste(round(Agreement*100,0),"%",sep = ""),color=-Agreement),size=3) + 
  scale_y_discrete(labels=substring(unique(ourMeasure$Question),0,20)) + 
  scale_x_discrete(labels=substring(unique(ourMeasure$Task),0,10)) + 
  theme(legend.position="none",axis.text.x = element_text(angle = 45, hjust = 1))

```
