---
title: "clean_task_map_visuals"
output: html_notebook
---

```{r}
library(factoextra)
library(NbClust)
library(cluster)
library(svglite)
library(ggplot2)
library(dplyr)
library(tidyverse)
```

# Load the Data
```{r}
task_map <- read_csv('../../data/task_map.csv')
```

# Plot the Task Map

Draw the task map using PCA & clustering

First, run the PCA
```{r, fig.width=16, fig.height=5}
set.seed(1)

pca <- task_map %>% #select(-continuous_questions) %>%
  select(-task) %>%
  prcomp(center = T)

# get optimal number of clusters -- "silhouette" method
fviz_nbclust(x = pca$x, FUNcluster = stats::kmeans, method = "silhouette") +
  labs(subtitle = "Silhouette method")

# get optimal number of clusters
NbClust(data = pca$x, distance = "euclidean",
        min.nc = 2, max.nc = 15, method = "kmeans")

kmeans_output <- pca$x %>% 
  kmeans(centers = 3, nstart = 100)

combined_data <- cbind(task_map,
      pca$x, factor(kmeans_output$cluster)) %>%
  rename(cluster = `factor(kmeans_output$cluster)`)

fviz_eig(pca)
```

Standard Task Map Image with All Labels
```{r, fig.width=14, fig.height=5}
p <- combined_data %>%
  ggplot(aes(
    x = PC1,
    y = PC2,
    label = task,
    fill = cluster
  )) + geom_point() + geom_label(nudge_y = 0.1, size = 4) +

 theme_light(base_size = 24)

p

ggsave(plot = p, filename = '../../outputs/task-map.png')
```


# Task Map with McGrath Labels for interpretability
```{r}
task_map_with_intuitive_labels <- read_csv('../../data/figure_2_intuitive_interpretation/task_map_with_intuitive_hand_groupings.csv') %>%
  mutate(
    group = as.factor(group)
  )
```

```{r, fig.width=14, fig.height=5}
combined_data_with_labels <- combined_data %>%
    left_join(task_map_with_intuitive_labels, by = "task") %>%
    rename(`McGrath Quadrant` = group)

mcgrath_quad_display_set <- c(
    "Whac-A-Mole",
    "Space Fortress",
    "Search for Oil Task",
    "Target Search",
    "9 Dot Problem",
    "Ravens Matrices",
    "Moral Reasoning (Disciplinary Action Case)",
    "Allocating resources to programs",
    "hk_22482ca42486c72f writing",
    "Writing story",
    "Word construction from a subset of letters",
    "Word completion given starting letter",
    "Shopping plan",
    "Mock jury",
    "Ultimatum game (various versions)",
    "Dictator game and its variants",
    "Pharmaceutical Company (hidden-profile)",
    "Investment game (hidden-profile)"
)

p <- combined_data_with_labels %>%
    ggplot(aes(x = PC1,
               y = PC2,
               label = task,
               color = `McGrath Quadrant`
               )) +
    geom_point(alpha = 0.4) +
    geom_label(data = subset(combined_data_with_labels, task %in% mcgrath_quad_display_set),
               aes(label = task, fill = `McGrath Quadrant`),
               vjust = "inward",
               hjust = "inward",
               color = "white",
               size = 2.5,
               fontface = "bold") +
    geom_point(data = subset(combined_data_with_labels, task %in% mcgrath_quad_display_set),
               aes(label = task, fill = `McGrath Quadrant`),
               vjust = "inward",
               hjust = "inward",
               color = "black") +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(face = "bold")) +
    labs(x = "Demonstrable Correctness (PC1)",
         y = "Collaboration-Conflict (PC2)",
         title = "Projection of the Task Space in 2D (using PCA), with Illustrative Tasks") +
    scale_fill_hue(l = 45)

# Save the plot as an .svg file
ggsave(
    plot = p,
  filename = "../../outputs/figure_2_intuitive_interpretation/task_map_with_intuitive_illustrations_raw.svg",
    width = 14,
    height = 5,
    device = "svg"
)

p
```

# Task Map Showing Maximum- and Minimum-ally Different Task Sets
```{r}
# A set of the tasks that are most different
# this set has no restrictions
max_diff_set <- c('Railroad Route Construction game (Impossible Version)',
 'Reproducing arts',
 'Best job candidate (hidden-profile)',
 'Putting food into categories',
 'Checkers',
 'Minimal Group Paradigm (study diversity)',
 'Whac-A-Mole',
 '9 Dot Problem',
 'Shopping plan',
 'TOPSIM - general mgmt business game')

# A set of tasks that are the most similar
# No restrictions on this set
min_diff_set <- c('Arithmetic problem 1',
 'Euclidean traveling salesperson',
 'Abstract grid task',
 'Mastermind',
 'Logic Problem',
 'Guessing the correlation',
 'Random dot motion',
 'Letters-to-numbers problems (cryptography)',
 'Computer maze',
 'Recall images')
```
```{r, fig.width=14, fig.height=5}
 combined_data_with_labels <- combined_data %>%
    mutate(
        point_group = ifelse(task %in% max_diff_set, 'Most Different Tasks',
                             ifelse(task %in% min_diff_set, 'Most Similar Tasks', NA))
    )
  
p <- combined_data_with_labels %>%
    ggplot(aes(x = PC1,
               y = PC2,
               )) +
    geom_point(alpha = 0.4) +
    geom_label(data = subset(combined_data_with_labels, task %in% c(max_diff_set, min_diff_set)),
               aes(label = task, fill = point_group),
               hjust = "inward",
               color = "white",
               size = 2.5,
               fontface = "bold") +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(face = "bold")) +
    labs(x = "Demonstrable Correctness (PC1)",
         y = "Collaboration-Conflict (PC2)",
         title = "Projection of the Task Space in 2D (using PCA), with Illustrative Tasks") +
    scale_fill_hue(l = 45)

# Save the plot as an .svg file
ggsave(
    plot = p,
  filename = "../../outputs/figure_3_task_selection/Similar-Different-Dense-Sparse_raw.svg",
    width = 14,
    height = 5,
    device = "svg"
)

p
```

# Simulation of 10-Task Study + Plot the Support Vector Machine
```{r}
# This is the set that you can actually play as individual + as a group
# Removes the impossible version of the railroad game and all economic games

# In our hypothetical scenario, the researcher chooses these as the 10 tasks to study
max_diff_no_economicGames <- c(
'Writing story',
 '9 Dot Problem',
 'Word construction from a subset of letters',
 'Image rating',
 'Checkers',
 'Run a mini business',
 'Typing game',
 'Whac-A-Mole',
 'Divergent Association Task',
 'Carter Racing'
)
```

Create synthetic dependent variable based on the clusters
```{r}
tasks_with_dv <- subset(combined_data, task %in% max_diff_no_economicGames) %>%
  mutate(
    synergy = as.factor(ifelse(cluster == 1 | cluster == 2, 1, 0))
  )
combined_data <- combined_data %>%
  mutate(
    synergy = as.factor(ifelse(cluster == 1 | cluster == 2, 1, 0))
  )

# Save this so that we can run the real SVM in Python!
combined_data %>% 
  # rename columns in a more pretty format
  rename(
    `Conceptual-Behavioral` = Q1concept_behav,
    `Type 1 (Planning)` = Q3type_1_planning,
    `Type 2 (Generate)` = Q4type_2_generate,
    `Type 5 (Cognitive Conflict)` = Q6type_5_cc,
    `Type 7 (Battle)` = Q7type_7_battle,
    `Type 8 (Performance)` = Q8type_8_performance,
    `Divisible-Unitary` = Q9divisible_unitary,
    `Maximizing` = Q10maximizing,
    `Optimizing` = Q11optimizing,
    `Outcome Multiplicity` = Q13outcome_multip,
    `Solution Scheme Multiplicity` = Q14sol_scheme_mul,
    `Decision Verifiability` = Q15dec_verifiability,
    `Shared Knowledge` = Q16shared_knowledge,
    `Within-System Solution` = Q17within_sys_sol,
    `Answer Recognizability` = Q18ans_recog,
    `Time Solvability` = Q19time_solvability,
    `Type 3 and Type 4 (Objective Correctness)` = Q20type_3_type_4,
    `Conflicting Tradeoffs` = Q22confl_tradeoffs,
    `Solution Scheme Outcome Uncertainty` = Q23ss_out_uncert,
    `Eureka Question` = Q24eureka_question,
    `Intellectual-Manipulative` = Q2intel_manip_1,
    `Intellective-Judgmental` = Q21intellective_judg_1,
    `Creativity Input` = Q5creativity_input_1,
    `Type 6 (Mixed-Motive)` = Q25_type6_mixed_motive
  ) %>%
  write_csv('tasks_with_synthetic_data.csv')
```

The SVM Plotted here is fitted on just PC1 and PC2 for visualization purposes, but the 
"real" SVM that we fit and test (done in Python) in the file `svm_with_synthetic_data.ipynb`
is fit on the full data.

Decision boundary plotting code from: https://mhahsler.github.io/Introduction_to_Data_Mining_R_Examples/book/classification-alternative-techniques.html#k-nearest-neighbors
```{r decisionplot}
decisionplot <- function(model, data, class_var, 
  predict_type = c("class", "prob"), resolution = 5 * 75) {
  # resolution is set to 75 dpi if the image is rendered  5 inches wide. 
  
  y <- data %>% pull(class_var)
  x <- data %>% dplyr::select(-all_of(class_var))
  
  # resubstitution accuracy
  prediction <- predict(model, x, type = predict_type[1])
  # LDA returns a list
  if(is.list(prediction)) prediction <- prediction$class
  prediction <- factor(prediction, levels = levels(y))
  
  cm <- confusionMatrix(data = prediction, reference = y)
  acc <- cm$overall["Accuracy"]
  
  # evaluate model on a grid
  r <- sapply(x[, 1:2], range, na.rm = TRUE)
  xs <- seq(r[1,1], r[2,1], length.out = resolution)
  ys <- seq(r[1,2], r[2,2], length.out = resolution)
  g <- cbind(rep(xs, each = resolution), rep(ys, time = resolution))
  colnames(g) <- colnames(r)
  g <- as_tibble(g)
  
  ### guess how to get class labels from predict
  ### (unfortunately not very consistent between models)
  cl <- predict(model, g, type = predict_type[1])
  
  # LDA returns a list
  if(is.list(cl)) { 
    prob <- cl$posterior
    cl <- cl$class
  } else
    try(prob <- predict(model, g, type = predict_type[2]))
  
  # we visualize the difference in probability/score between the 
  # winning class and the second best class.
  # don't use probability if predict for the classifier does not support it.
  max_prob <- 1
  try({
    max_prob <- t(apply(prob, MARGIN = 1, sort, decreasing = TRUE))
    max_prob <- max_prob[,1] - max_prob[,2]
  }, silent = TRUE) 
  
  cl <- factor(cl, levels = levels(y))
  
  g <- g %>% add_column(prediction = cl, probability = max_prob)
  
  ggplot(g, mapping = aes_string(
    x = colnames(g)[1],
    y = colnames(g)[2])) +
    geom_raster(mapping = aes(fill = prediction, alpha = probability)) +
     geom_contour(mapping = aes(z = as.numeric(prediction)), 
      bins = length(levels(cl)), size = .5, color = "black") +
    geom_point(data = data, mapping =  aes_string(
      x = colnames(data)[1],
      y = colnames(data)[2],
      shape = class_var), alpha = .7) + 
    scale_alpha_continuous(range = c(0,1), limits = c(0,1), guide = "none") +  
    labs(subtitle = paste("Training accuracy:", round(acc, 2)))
}
```

```{r}
x <- combined_data %>% select(PC1, PC2, synergy, task)
train <- tasks_with_dv %>% select(PC1, PC2, synergy, task)
model <- train %>% svm(synergy ~ PC1 + PC2, data = ., kernel = "linear")

svmplot <- decisionplot(model, x, class_var = "synergy") + 
  geom_point(data = train, aes(x = PC1, y = PC2, shape = synergy, size = 5), color = "darkolivegreen2", show.legend = F) +
  geom_label(data = train, aes(label = task ), nudge_y = 0.2, size = 3) +
  labs(title = "SVM (Linear Kernel)") +
  theme_minimal(base_size = 12)

svmplot
  
ggsave('../figure_4_visualize_boundary_conditions/svmplot_synthetic_data_raw.svg', width = 12, height = 5, device = "svg")
```

