---
title: "generate_task_map_from_raw.Rmd"
author: "Emily Hu"
date: "06/21/2023"
output: html_document
---

This notebook takes in the raw Task Map Rater Data and cleans it into the Task Map.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```

# Read in the Task Map
Read in our saved version of the task map.
```{r}
df.mapping.raw <- read_csv('../../data/raw_map.csv')
```

First, store the names of the questions.
```{r}
# Question names
main_questions <- c(
  "Q1concept_behav",
  "Q2intel_manip_1",
  "Q3type_1_planning",
  "Q4type_2_generate",
  "Q5creativity_input_1",
  "Q6type_5_cc",
  "Q7type_7_battle",
  "Q8type_8_performance",
  "Q9divisible_unitary",
  "Q10maximizing",
  "Q11optimizing",
  "Q13outcome_multip",
  "Q14sol_scheme_mul",
  "Q15dec_verifiability",
  "Q16shared_knowledge",
  "Q17within_sys_sol",
  "Q18ans_recog",
  "Q19time_solvability",
  "Q20type_3_type_4",
  "Q21intellective_judg_1",
  "Q22confl_tradeoffs",
  "Q23ss_out_uncert",
  "Q24eureka_question"
)

continuous_questions <- c('Q2intel_manip_1',
                          'Q21intellective_judg_1','Q5creativity_input_1') 
```

```{r}
# Before mapping the tasks, filter to ONLY the most recent blob
# blobs indicate the version of the writeup, so raters who rated different 'blobs'
# rated different versions.

tasks_blobs_and_ids <- df.mapping.raw %>%
  select(task, task_blob_url, updatedAt) %>%
  arrange(desc(updatedAt))
  
most_recent_blob_urls <- tasks_blobs_and_ids %>% distinct(task, .keep_all = T)
  
df.mapping.raw <- df.mapping.raw %>%
  filter(task_blob_url %in% most_recent_blob_urls$task_blob_url)
```

Separately calculate categorical and numeric, as categories need to be converted to 1&0
```{r}
categorical <- df.mapping.raw %>%
  select(c(main_questions, task, task_blob_url)) %>%
  select(-continuous_questions) %>%
  pivot_longer(cols = -c(task, task_blob_url), names_to = "question_name") %>%
  mutate(value = recode(value, 
                     "Mental" = 0,
                     "Physical" = 1,
                    # "Not applicable or not answerable based on the task description (Please Elaborate Below.)" = 3,
                     "No" = 0,
                     "Yes" = 1
                   )) %>%
  group_by(question_name, task, task_blob_url) %>%
  mutate(
    value = mean(value, na.rm = T)
  ) %>% unique() %>%
  pivot_wider(values_from = "value", names_from = "question_name")

numeric <- df.mapping.raw %>%
  select(c(continuous_questions, task, task_blob_url)) %>%
  pivot_longer(cols = -c(task, task_blob_url), names_to = "question_name") %>%
   group_by(question_name, task, task_blob_url) %>%
  mutate(
    value = mean(as.numeric(value), na.rm = T)
  ) %>% unique() %>%
  pivot_wider(values_from = c("value"), names_from = "question_name")
  
task_map <- inner_join(categorical, numeric, by = c("task", "task_blob_url")) %>% ungroup() %>%
  select(-task_blob_url) # remove task blob for main task map export
```

# Add in McGrath Type 6, which is rated by hand
These are games in which different players take on different roles, which means that it is not possible for individuals to play this game by themselves (e.g., a team is required).

Since our original research question required the study of "synergy" (comparing the performance of individuals/nominal teams to that of teams), we manually filtered out tasks that could not be played by solo players, and then added them back. This is why the `mixed_motive_tasks` dimension has to be added in separately.
```{r}
#mixed-motive tasks
mixed_motive_tasks = c(
        "Arithmetic problem 2",
        "Pharmaceutical Company (hidden-profile)",
        "New Recruit",
        "Iterated Snowdrift Game (Without Punishment)",
        "Iterated Snowdrift Game (With Punishment)",
        "Blocks World for Teams",
        "The beer game",
        "Mock jury",
        "Investment Game (aka Trust Game)",
        "TOPSIM - general mgmt business game",
        "Oligopoly game",
        "Minimal Group Paradigm (study diversity)",
        "Organization Game",
        "Biopharm Seltek",
        "Bullard Houses",
        "Apache helicopter flight simulator (Longbow2)",
        "Sender-Receiver game",
        "Volunteer Investment Game",
        "Ultimatum game (various versions)",
        "Prisoner's Dilemma (various versions)",
        "Public goods game",
        "Best job candidate (hidden-profile)",
        "Aerospace Investment (Role-playing)",
        "Find the common symbol",
        "Battle of the sexes",
        "Investment game (hidden-profile)",
        "Dictator game and its variants",
        "Intergroup Prisoner's Dilemma",
        "Chicken",
        "Minimum-effort tacit coordination game"
)

task_map <- task_map %>%
  mutate(
    Q25_type6_mixed_motive = ifelse(task %in% mixed_motive_tasks, 1,0)    
  )
```

# Export the Task Map
```{r}
task_map %>% write_csv('../task_map.csv')
```