title: "generate_task_map_from_raw.Rmd"
author: "Emily Hu"
date: "06/21/2023"
output:
  html_document:
    dev: png
    fig_width: 8
    fig_height: 5

This notebook takes in the raw Task Map Rater Data and cleans it into the Task Map.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```

# Read in the Task Map
Read in our saved version of the task map.
```{r}
df.mapping.raw <- read_csv('../../data/raw_map.csv')
```

First, store the names of the questions.
```{r}
# Question names
main_questions <- c(
  "Q1concept_behav",
  "Q2intel_manip_1",
  "Q3type_1_planning",
  "Q4type_2_generate",
  "Q5creativity_input_1",
  "Q6type_5_cc",
  "Q7type_7_battle",
  "Q8type_8_performance",
  "Q9divisible_unitary",
  "Q10maximizing",
  "Q11optimizing",
  "Q13outcome_multip",
  "Q14sol_scheme_mul",
  "Q15dec_verifiability",
  "Q16shared_knowledge",
  "Q17within_sys_sol",
  "Q18ans_recog",
  "Q19time_solvability",
  "Q20type_3_type_4",
  "Q21intellective_judg_1",
  "Q22confl_tradeoffs",
  "Q23ss_out_uncert",
  "Q24eureka_question"
)

continuous_questions <- c('Q2intel_manip_1',
                          'Q21intellective_judg_1','Q5creativity_input_1') 

pretty_name_lookup <- c(
  "Q1concept_behav" = "Conceptual-Behavioral",
  "Q3type_1_planning" = "Type 1 (Planning)",
  "Q4type_2_generate" = "Type 2 (Generate)",
  "Q6type_5_cc" = "Type 5 (Cognitive Conflict)",
  "Q7type_7_battle" = "Type 7 (Battle)",
  "Q8type_8_performance" = "Type 8 (Performance)",
  "Q9divisible_unitary" = "Divisible-Unitary",
  "Q10maximizing" = "Maximizing",
  "Q11optimizing" = "Optimizing",
  "Q13outcome_multip" = "Outcome Multiplicity",
  "Q14sol_scheme_mul" = "Solution Scheme Multiplicity",
  "Q15dec_verifiability" = "Decision Verifiability",
  "Q16shared_knowledge" = "Shared Knowledge",
  "Q17within_sys_sol" = "Within-System Solution",
  "Q18ans_recog" = "Answer Recognizability",
  "Q19time_solvability" = "Time Solvability",
  "Q20type_3_type_4" = "Type 3 and Type 4 (Objective Correctness)",
  "Q22confl_tradeoffs" = "Conflicting Tradeoffs",
  "Q23ss_out_uncert" = "Solution Scheme Outcome Uncertainty",
  "Q24eureka_question" = "Eureka Question",
  "Q2intel_manip_1" = "Intellectual-Manipulative",
  "Q21intellective_judg_1" = "Intellective-Judgmental",
  "Q5creativity_input_1" = "Creativity Input",
  "Q25_type6_mixed_motive" = "Type 6 (Mixed-Motive)"
)

pretty_name_order <- c(
  "Conceptual-Behavioral",
  "Type 1 (Planning)",
  "Type 2 (Generate)",
  "Type 5 (Cognitive Conflict)",
  "Type 7 (Battle)",
  "Type 8 (Performance)",
  "Divisible-Unitary",
  "Maximizing",
  "Optimizing",
  "Outcome Multiplicity",
  "Solution Scheme Multiplicity",
  "Decision Verifiability",
  "Shared Knowledge",
  "Within-System Solution",
  "Answer Recognizability",
  "Time Solvability",
  "Type 3 and Type 4 (Objective Correctness)",
  "Conflicting Tradeoffs",
  "Solution Scheme Outcome Uncertainty",
  "Eureka Question",
  "Intellectual-Manipulative",
  "Intellective-Judgmental",
  "Creativity Input",
  "Type 6 (Mixed-Motive)"
)
```

```{r}
# Before mapping the tasks, filter to ONLY the most recent blob
# blobs indicate the version of the writeup, so raters who rated different 'blobs'
# rated different versions.

tasks_blobs_and_ids <- df.mapping.raw %>%
  select(task, task_blob_url, updatedAt) %>%
  arrange(desc(updatedAt))
  
most_recent_blob_urls <- tasks_blobs_and_ids %>% distinct(task, .keep_all = T)
  
df.mapping.raw <- df.mapping.raw %>%
  filter(task_blob_url %in% most_recent_blob_urls$task_blob_url)
```

Separately calculate categorical and numeric, as categories need to be converted to 1&0
```{r}
categorical <- df.mapping.raw %>%
  select(c(main_questions, task, task_blob_url)) %>%
  select(-continuous_questions) %>%
  pivot_longer(cols = -c(task, task_blob_url), names_to = "question_name") %>%
  mutate(value = recode(value, 
                     "Mental" = 0,
                     "Physical" = 1,
                    # "Not applicable or not answerable based on the task description (Please Elaborate Below.)" = 3,
                     "No" = 0,
                     "Yes" = 1
                   )) %>%
  group_by(question_name, task, task_blob_url) %>%
  mutate(
    value = mean(value, na.rm = T)
  ) %>% unique() %>%
  pivot_wider(values_from = "value", names_from = "question_name")

numeric <- df.mapping.raw %>%
  select(c(continuous_questions, task, task_blob_url)) %>%
  pivot_longer(cols = -c(task, task_blob_url), names_to = "question_name") %>%
   group_by(question_name, task, task_blob_url) %>%
  mutate(
    value = mean(as.numeric(value), na.rm = T)
  ) %>% unique() %>%
  pivot_wider(values_from = c("value"), names_from = "question_name")
  
task_map <- inner_join(categorical, numeric, by = c("task", "task_blob_url")) %>% ungroup() %>%
  select(-task_blob_url) # remove task blob for main task map export
```

# Add in McGrath Type 6, which is rated by hand
These are games in which different players take on different roles, which means that it is not possible for individuals to play this game by themselves (e.g., a team is required).

Since our original research question required the study of "synergy" (comparing the performance of individuals/nominal teams to that of teams), we manually filtered out tasks that could not be played by solo players, and then added them back. This is why the `mixed_motive_tasks` dimension has to be added in separately.
```{r}
#mixed-motive tasks
mixed_motive_tasks = c(
        "Arithmetic problem 2",
        "Pharmaceutical Company (hidden-profile)",
        "New Recruit",
        "Iterated Snowdrift Game (Without Punishment)",
        "Iterated Snowdrift Game (With Punishment)",
        "Blocks World for Teams",
        "The beer game",
        "Mock jury",
        "Investment Game (aka Trust Game)",
        "TOPSIM - general mgmt business game",
        "Oligopoly game",
        "Minimal Group Paradigm (study diversity)",
        "Organization Game",
        "Biopharm Seltek",
        "Bullard Houses",
        "Apache helicopter flight simulator (Longbow2)",
        "Sender-Receiver game",
        "Volunteer Investment Game",
        "Ultimatum game (various versions)",
        "Prisoner's Dilemma (various versions)",
        "Public goods game",
        "Best job candidate (hidden-profile)",
        "Aerospace Investment (Role-playing)",
        "Find the common symbol",
        "Battle of the sexes",
        "Investment game (hidden-profile)",
        "Dictator game and its variants",
        "Intergroup Prisoner's Dilemma",
        "Chicken",
        "Minimum-effort tacit coordination game"
)

task_map <- task_map %>%
  mutate(
    Q25_type6_mixed_motive = ifelse(task %in% mixed_motive_tasks, 1,0)    
  )

task_map <- task_map %>%
  rename(!!!setNames(names(pretty_name_lookup), pretty_name_lookup)) %>%
  select(task, all_of(pretty_name_order))
```

# Bootstrapped IRR Analysis
```{r}
library(purrr)
library(tidyr)
library(ggplot2)
library(stringr)

set.seed(2023)

rater_candidates <- c("rater_id","rater","user_id","worker_id","respondent_id","respondent","email","mturk_id","worker","user")
rater_col <- intersect(names(df.mapping.raw), rater_candidates) %>% first()

# Keep only question names that actually exist in df.mapping.raw

available_questions <- intersect(main_questions, names(df.mapping.raw))
missing_questions <- setdiff(main_questions, available_questions)
if(length(missing_questions) > 0){
message("These question columns do not exist in df.mapping.raw and will be skipped:\n",
paste(missing_questions, collapse = ", "))
}
main_questions_use <- available_questions

if(is.null(rater_col) || length(rater_col)==0){
df.mapping.raw <- df.mapping.raw %>% mutate(.respondent_row = row_number())
rater_col <- ".respondent_row"
}

crowd_questions <- setdiff(pretty_name_order, "Type 6 (Mixed-Motive)")

# ORIGINAL AGGREGATE: compute the original mean per task × question from the raw rater rows
orig_agg <- df.mapping.raw %>%
  mutate(across(-c(task, !!sym(rater_col)), as.character)) %>%   # ← FIX: convert ALL question columns
  select(any_of(c("task", rater_col, main_questions_use))) %>%
  pivot_longer(
    cols = -all_of(c("task", rater_col)),
    names_to = "question_name",
    values_to = "value"
  ) %>%
  mutate(value = recode(value,
                        "Mental" = 0,
                        "Physical" = 1,
                        "No" = 0,
                        "Yes" = 1)) %>%
  mutate(value = as.numeric(value)) %>%
  group_by(task, question_name) %>%
  summarize(orig_mean = mean(value, na.rm = TRUE), .groups = "drop") %>%
  left_join(
    tibble(
      question_name = names(pretty_name_lookup),
      pretty = pretty_name_lookup[names(pretty_name_lookup)]
    ),
    by = "question_name"
  ) %>%
  mutate(pretty = coalesce(pretty, question_name)) %>%
  filter(pretty %in% crowd_questions)

# ---------------------------------------------------------
# Bootstrap section (fully fixed)
# ---------------------------------------------------------

boot_results <- vector("list", n_boot)

for(i in seq_len(n_boot)) {

  sampled_ids <- sample(unique_raters, n_raters_sample, replace = TRUE)

  boot_df <- map_dfr(
    sampled_ids,
    ~ df.mapping.raw %>% filter((!!rlang::sym(rater_col)) == .x)
  )

  # Force all relevant question columns to character
  boot_df_chr <- boot_df %>%
    mutate(across(any_of(main_questions_use), as.character))

  boot_long <- boot_df_chr %>%
    select(any_of(c("task", main_questions_use))) %>%
    pivot_longer(
      cols = -task,
      names_to = "question_name",
      values_to = "value"
    ) %>%
    # Keep only the primary categorical answers you want
    mutate(
      value = na_if(value, ""),   # remove blanks
      value = ifelse(value %in% c("Yes","No","Physical","Mental"), value, NA_character_)
    ) %>%
    filter(!is.na(value)) %>%
    # Safe recode with default NA
    mutate(
      value = dplyr::recode(
        value,
        "Mental"   = "0",
        "Physical" = "1",
        "No"       = "0",
        "Yes"      = "1",
        .default   = NA_character_
      ),
      value = as.numeric(value)
    ) %>%
    group_by(task, question_name) %>%
    summarize(mean_value = mean(value, na.rm = TRUE), .groups = "drop") %>%
    left_join(
      tibble(
        question_name = names(pretty_name_lookup),
        pretty = pretty_name_lookup[names(pretty_name_lookup)]
      ),
      by = "question_name"
    ) %>%
    mutate(pretty = coalesce(pretty, question_name)) %>%
    filter(pretty %in% crowd_questions)

  boot_results[[i]] <- boot_long %>% mutate(iter = i)
}

boot_all <- bind_rows(boot_results)

# attach original means and compute differences
boot_all_diff <- boot_all %>%
  left_join(
    orig_agg %>% select(task, pretty, orig_mean),
    by = c("task", "pretty")
  ) %>%
  mutate(diff_from_orig = mean_value - orig_mean)

# ---------------------------------------------------------
# Compute CIs
# ---------------------------------------------------------

cis <- boot_all_diff %>%
  group_by(task, pretty) %>%
  summarize(
    lower = quantile(diff_from_orig, probs = 0.025, na.rm = TRUE),
    upper = quantile(diff_from_orig, probs = 0.975, na.rm = TRUE),
    boot_mean = mean(diff_from_orig, na.rm = TRUE),
    orig_mean = first(orig_mean),
    .groups = "drop"
  ) %>%
  mutate(ci_width = upper - lower)

# ---------------------------------------------------------
# Summary by question (UPDATED)
# ---------------------------------------------------------

ci_summary_by_column <- boot_all_diff %>%
  group_by(pretty) %>%
  summarize(
    n_tasks = n_distinct(task),
    mean_difference = mean(diff_from_orig, na.rm = TRUE),
    sd_difference = sd(diff_from_orig, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(
    cis %>%
      group_by(pretty) %>%
      summarize(
        mean_ci_width = mean(ci_width, na.rm = TRUE),
        median_ci_width = median(ci_width, na.rm = TRUE),
        max_ci_width = max(ci_width, na.rm = TRUE),
        pct_wide_gt_0_2 = mean(ci_width > 0.2, na.rm = TRUE),
        .groups = "drop"
      ),
    by = "pretty"
  ) %>%
  arrange(desc(sd_difference))

# ---------------------------------------------------------
# Save outputs
# ---------------------------------------------------------

dir.create("../../outputs/processed_data", recursive = TRUE, showWarnings = FALSE)
dir.create("../../outputs/figures", recursive = TRUE, showWarnings = FALSE)

write_csv(ci_summary_by_column, "../../outputs/processed_data/ci_summary_by_column.csv")
write_csv(cis, "../../outputs/processed_data/task_question_bootstrap_cis.csv")

# ---------------------------------------------------------
# PREPARATION: Calculate Mean Absolute Difference (Instability)
# ---------------------------------------------------------

# 1. Calculate the Mean Absolute Difference for every task/dimension
#    Formula: Average of |Bootstrap Mean - Original Mean|
#    Interpretation: "On average, how far does a new sample drift from the original?"
task_instability_by_dim <- boot_all_diff %>%
  group_by(pretty, task) %>%
  summarize(
    # We use abs() because we care about the MAGNITUDE of the change
    mean_abs_diff = mean(abs(diff_from_orig), na.rm = TRUE),
    .groups = "drop"
  )

# 2. Sort Dimensions (Y-axis)
#    We sort by the Median Instability.
#    Top of plot = Dimensions most likely to change (Unstable).
#    Bottom of plot = Dimensions that stay the same (Stable).
dim_order_instability <- task_instability_by_dim %>%
  group_by(pretty) %>%
  summarize(median_instability = median(mean_abs_diff, na.rm = TRUE)) %>%
  arrange(median_instability) %>% 
  pull(pretty)

task_instability_by_dim <- task_instability_by_dim %>%
  mutate(pretty = factor(pretty, levels = dim_order_instability))

# ---------------------------------------------------------
# PLOT: Raincloud of Instability
# ---------------------------------------------------------

p_raincloud_mad <- ggplot(task_instability_by_dim, aes(x = mean_abs_diff, y = pretty)) +
  
  # 1. Density Ridges (Shows the shape of instability for the dimension)
  ggridges::geom_density_ridges(
    aes(fill = pretty),
    jittered_points = TRUE,       # Adds the tick marks for tasks
    position = ggridges::position_points_jitter(
      width = 0.001, height = 0   # Tiny jitter to separate overlapping lines slightly
    ),
    point_shape = '|',            # Vertical tick marks
    point_size = 2,               # Mark size
    point_alpha = 0.6,            # Transparency
    alpha = 0.7,                  # Ridge transparency
    scale = 0.9
  ) +
  
  # 2. Formatting
  labs(
    x = "Mean Absolute Difference (Avg distance from Original Mean)",
    y = "Task Dimension",
    title = "Task Stability Map: Magnitude of Change",
    subtitle = "Each '|' mark is one Task.\nValues further right indicate tasks that change drastically based on the rater sample."
  ) +
  
  theme_minimal() +
  theme(
    text = element_text(family = "Times New Roman", size = 12),
    legend.position = "none",
    axis.text.y = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )

# ---------------------------------------------------------
# Save
# ---------------------------------------------------------

ggsave("../../outputs/figures/task_map_absolute_diff_raincloud.png",
       p_raincloud_mad, width = 10, height = 12, units = "in", dpi = 300)

print(p_raincloud_mad)

```


# Export the Task Map
```{r}
# write task map into the repository `outputs/` folder (ensures we don't modify `data/`)
task_map %>% write_csv('../../outputs/processed_data/task_map.csv')
```