---
title: "new-task-mapping"
author: "Emily Hu"
date: "5/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(factoextra)
library(plotly)
library(irr)
library(anytime)
library(dplyr)
library(tidyverse)
```

```{r}
df.mapping.raw <- read_delim('http://task-robot.glitch.me/results/survey/csv')
```

Ensure we don't have any accidental resubmissions -- sometimes the server logs a "double click" as two separate maps!

```{r}
df.mapping.raw <- distinct(df.mapping.raw, user, task, .keep_all = T)
nrow(df.mapping.raw)
```
# Save the Raw Data

```{r}
df.mapping.raw %>% write_csv('../raw_map.csv')
```

# Create a CSV of workers to pay in `survey_workflows` with WorkerID, date, how many tasks they did, whether they've been paid for it

```{r}
# The same spreadsheet logs how much we previously paid; we read this in and update
df.payment.prev <- read_csv('../survey_workflows/mapper_payment.csv') %>% 
  select(WorkerId, amount_paid, last_payment_date)

# First, we keep track of everyone's cumulative payments
df.mapping.payment <- df.mapping.raw %>%
  select(
    user, updatedAt
  ) %>%
  mutate(
    pay = 3, # flat rate of $3 per task
    paid = 0
  ) %>%
  group_by(user) %>%
  summarize(
    lastUpdate = last(updatedAt),
    payment = sum(pay),
    num_tasks_completed = payment/3
  ) %>% rename(WorkerId = user)

# Then we subtract off how much they have already been paid
df.mapping.payment.new <- df.mapping.payment %>% left_join(df.payment.prev, by = "WorkerId") %>%
   mutate(
     amount_paid = ifelse(is.na(amount_paid), 0, amount_paid)
   ) %>%
  mutate(
    amount_to_pay = payment - amount_paid
  )

df.mapping.payment.new %>% write_csv('../survey_workflows/mapper_payment.csv')
```

# Take a look at the Task Map Itself
```{r}
# Question names
main_questions <- c(
  "Q1concept_behav",
  "Q2intel_manip_1",
  "Q3type_1_planning",
  "Q4type_2_generate",
  "Q5creativity_input_1",
  "Q6type_5_cc",
  "Q7type_7_battle",
  "Q8type_8_performance",
  "Q9divisible_unitary",
  "Q10maximizing",
  "Q11optimizing",
  "Q13outcome_multip",
  "Q14sol_scheme_mul",
  "Q15dec_verifiability",
  "Q16shared_knowledge",
  "Q17within_sys_sol",
  "Q18ans_recog",
  "Q19time_solvability",
  "Q20type_3_type_4",
  "Q21intellective_judg_1",
  "Q22confl_tradeoffs",
  "Q23ss_out_uncert",
  "Q24eureka_question"
)

continuous_questions <- c('Q2intel_manip_1',
                          'Q21intellective_judg_1','Q5creativity_input_1') 
```

```{r}
df.main_questions_summary <- df.mapping.raw %>%
  select(c(main_questions, task, task_blob_url)) %>%
  select(-continuous_questions) %>%
  pivot_longer(cols = -c(task,task_blob_url), names_to = "question_name") %>%
  mutate(value = recode(value, 
                     "Mental" = 0,
                     "Physical" = 1,
                     "Not applicable or not answerable based on the task description (Please Elaborate Below.)" = 3,
                     "No" = 0,
                     "Yes" = 1
                   )) %>%
  filter(value != 3) %>% # remove cases in which people thought it wasn't answerable - for now
  group_by(task, task_blob_url, question_name) %>%
  summarize(mean_rating = mean(value, na.rm = T),
            n_labels = agree(t(value))$raters,
            all_values = paste(value, collapse = " & "),
            agreement = ifelse(mean_rating > 0.5, mean_rating, 1-mean_rating),
            general.alpha = (agreement-0.5)/(0.5)
            )
```

Look at at a per-question (or per-task) summary of basic agreement

```{r}
task_based_summary <- df.main_questions_summary %>%
  filter(n_labels > 1) %>%
  group_by(task, task_blob_url) %>% # can do task, question_name
  summarize(
    n_labels = round(mean(n_labels),0),
    mean_agreement = mean(agreement),
    mean_alpha = mean(general.alpha)
  ) %>%
  arrange(desc(mean_alpha))

task_based_summary
```

Export the task map

```{r}
# Before mapping the tasks, filter to ONLY the most recent blob
# If checking BETWEEN blobs, comment this out
tasks_blobs_and_ids <- df.mapping.raw %>%
  select(task, task_blob_url, updatedAt) %>%
  arrange(desc(updatedAt))
  
most_recent_blob_urls <- tasks_blobs_and_ids %>% distinct(task, .keep_all = T)
  
df.mapping.raw <- df.mapping.raw %>%
  filter(task_blob_url %in% most_recent_blob_urls$task_blob_url)
```

```{r}
categorical <- df.mapping.raw %>%
  select(c(main_questions, task, task_blob_url)) %>%
  select(-continuous_questions) %>%
  pivot_longer(cols = -c(task, task_blob_url), names_to = "question_name") %>%
  mutate(value = recode(value, 
                     "Mental" = 0,
                     "Physical" = 1,
                    # "Not applicable or not answerable based on the task description (Please Elaborate Below.)" = 3,
                     "No" = 0,
                     "Yes" = 1
                   )) %>%
  group_by(question_name, task, task_blob_url) %>%
  mutate(
    value = mean(value, na.rm = T)
  ) %>% unique() %>%
  pivot_wider(values_from = "value", names_from = "question_name")


numeric <- df.mapping.raw %>%
  select(c(continuous_questions, task, task_blob_url)) %>%
  pivot_longer(cols = -c(task, task_blob_url), names_to = "question_name") %>%
   group_by(question_name, task, task_blob_url) %>%
  mutate(
    value = mean(as.numeric(value), na.rm = T)
  ) %>% unique() %>%
  pivot_wider(values_from = c("value"), names_from = "question_name")
  
task_map <- inner_join(categorical, numeric, by = c("task", "task_blob_url")) %>% ungroup() %>%
  select(-task_blob_url) # remove task blob for main task map export

task_map %>% write_csv('../task_map.csv')
```

Special investigation into whether the (second) rewrite of Putting Food Into Categories helped

```{r}
# Commented this out because I've set the task map to take the most recent blob.

# new.writeup <- task_map %>%
#   filter(task_blob_url == "https://api.github.com/repos/Watts-Lab/task-mapping/git/blobs/18f592c297a321002458953433b2e96117c99ae7") %>% t()
# 
# old.writeup <- task_map %>%
#   filter(task_blob_url == "https://api.github.com/repos/Watts-Lab/task-mapping/git/blobs/871175e24910d4800931dd2e8bfbe14475b86343") %>% t()
# 
# new.writeup
# old.writeup
```

```{r, fig.width=12, fig.height=5}
set.seed(1)

pca <- task_map %>% #select(-continuous_questions) %>%
  select(-task) %>%
  prcomp()

kmeans <- pca$x %>%
  kmeans(centers = 4, nstart = 100)

combined_data <- cbind(task_map,
      pca$x, factor(kmeans$cluster)) %>%
  rename(cluster = `factor(kmeans$cluster)`)

p <- combined_data %>%
  ggplot(aes(
    x = PC1,
    y = PC2,
    label = task ,
    fill = cluster
  )) + geom_point() + geom_label(nudge_y = 0.1, size = 2)
p

plot_ly(
  x = combined_data$PC1,
  y = combined_data$PC2,
  z = combined_data$PC3,
  type = "scatter3d",
  mode = "markers", # can use mode = "text"
  text = combined_data$task ,
  color = combined_data$cluster
)

fviz_eig(pca)
ggsave(plot = p, filename = '../task-map.png')
```

# Set up Data Export for Karger's Algo

```{r}
df.karger <- df.mapping.raw %>%
  select(c(main_questions, task, user)) %>%
  select(-continuous_questions) %>%
  pivot_longer(cols = -c(task,user), names_to = "question_name") %>%
  mutate(
    value = recode(
      value,
      "Mental" = -1,
      "Physical" = 1,
      #"Not applicable or not answerable based on the task description (Please Elaborate Below.)" = 3,
      "No" = -1,
      "Yes" = 1
    )
  ) %>% ungroup() %>%
  select(user, question_name, task, value)

df.karger %>% write_csv('df_for_karger_MAIN.csv')
```

# How well did the people who showed up today do on the pre-test?
```{r}
previously_tested <- read_csv('../survey_workflows/previous_tested.csv')

df.rater_distribution <- df.mapping.payment %>%
  select(user, num_tasks_completed) %>%
  left_join(previously_tested, by = c("user" = "name")) %>%
  group_by(user) %>% # get rid of people who did the old pre-test
        arrange(user, desc(score_pct)) %>% 
        slice(1) %>%
  select(user, num_tasks_completed, score_pct) %>% ungroup() %>%
  group_by(score_pct) %>%
  summarize(num_workers = sum(num_tasks_completed))
  
ggplot(df.rater_distribution, aes(x = score_pct, y = num_workers)) +
  geom_bar(stat = "identity") +
  scale_x_binned()
```

Look at qualitative feedback about questions
```{r}
df.mapping.raw %>%
select(c(contains("elaboration"),task)) %>%
pivot_longer(cols = -task, names_to = "question_name") %>%
  drop_na() %>%
  filter(nchar(value) > 2) %>%
  filter(value != 'no problems.' & value != 'Nope') %>% # drop people who said like, 'no'
  arrange(question_name) %>% write_csv("./qual-feedbacks/task_mapping_feedback-main.csv")
```




